Document S1

### 2025-08-20 latex/docS1.tex
Updates from Overleaf

\subsection*{Identification of robust recombination events}
Before characterizing recombination events in detail, we sought to remove probable artifacts. 
Systematic errors in SARS-CoV-2 sequences associated with sequencing protocols have been documented (Turakhia et al., 2022), 
which can confound recombination detection (De Maio et al., 2024). 
By inspecting copying patterns at sites that differ between recombinant parents, 
we find a convincing signal when treating adjacent and near-adjacent sites as a single locus. 
Artifactual recombination events can be characterized as 
having fewer than four such loci supporting the left or right parent on either side of a putative breakpoint (STAR Methods). 
Of the 929 recombination events in the ARG, this measure identifies 543 as artifactual, 
leaving 386 “robust” events (Figure S1A). 
The copying patterns depicted in Figure S1B illustrate the genomic evidence for 
three recombination events identified as artifactual, compared to a marginally robust one.

@@

\subsection*{Additional analyses of the Pango Xs}
\subsubsection*{Multiple origins}
\subsubsection*{XS}
https://github.com/jeromekelleher/sc2ts-paper/issues/287
In the ARG, the XS samples appear to have originated from two sequential recombination events. 
However, the second event is likely an artifact, 
as the XS sample associated with this event failed the minimum net number of supporting loci. 
In addition, this sample was sequenced using the AmpliSeq V1 kit, 
which was also used to sequence eight other samples descending from the same event. 
We excluded this likely artifactual event from further analysis and 
consider XS to emerge from a single recombinant origin.

>>>>

\subsection*{Identification of robust recombination events}
Before characterizing recombination events in detail, we sought to remove probable artifacts. 
Systematic errors in SARS-CoV-2 sequences associated with sequencing protocols have been documented (Turakhia et al., 2022), 
which can confound recombination detection (De Maio et al., 2024). 
By inspecting copying patterns at sites that differ between recombinant parents, 
we find a convincing signal when treating adjacent and near-adjacent sites as a single locus. 
Artifactual recombination events can be characterized as 
having fewer than four such loci supporting the left or right parent on either side of a suggested breakpoint (STAR Methods). 
Of the 929 recombination events in the ARG, this measure identifies 543 as artifactual, 
leaving 386 “robust” events (Figure S1A). 
The copying patterns depicted in Figure S1B illustrate the genomic evidence for 
three recombination events identified as artifactual, compared to a marginally robust one.

@@

\subsection*{Additional analyses of the Pango Xs}
\subsubsection*{Multiple origins}
\subsubsection*{XS}
https://github.com/jeromekelleher/sc2ts-paper/issues/287
In the ARG, the XS samples appear to have originated from two sequential recombination events. 
However, the second event is likely an artifact, 
as the XS sample associated with this event failed the minimum net number of supporting loci. 
In addition, this sample was sequenced using the AmpliSeq V1 kit, 
which was also used to sequence eight other samples descending from the same event. 
We excluded this likely artifactual event from further analysis and 
consider XS to have emerged from a single recombinant origin.
